---
title: "ATM Cash Optimization"
author: "Sena Buwana"
date: "October 06, 2018"
output: pdf_document
---

requiring the libraries
```{r}
library('dplyr')
library('tseries')
library('xts')
library('zoo')
library('ggplot2')
library('fUnitRoots')
library('forecast')
library('MLmetrics')
```

Import the data set train
```{r}
atm.train <- read.csv('D:/Sena/Projects/Finhacks/atm_train.csv')
```

Processing the data and split into groups of ATMs
```{r}
atm.withdrawals <- atm.train %>% select(no..ATM,date,Withdrawals)
atm.grouped <- split(atm.withdrawals, f = atm.withdrawals$no..ATM)
```

Creating list of timeseries objects
A timeseries object contains date and daily withdrawal
```{r}
atm.ts <- list()
for (i in 1:10626) {
  temp.ts <- xts(atm.grouped[[i]]$Withdrawals, as.Date(atm.grouped[[i]]$date, format='%Y-%m-%d'))
  atm.ts[[i]] <- temp.ts
}
```

Split train dataset to new train dataset (10 weeks) and test dataset (remaining 1 week)
```{r}
atm.ts.train <- list()
atm.ts.test <- list()
for(i in 1:10626){
  atm.ts.train[[i]] <- first(atm.ts[[i]], '10 weeks')
  atm.ts.test[[i]] <- last(atm.ts[[i]], '1 week')
}
```


Perform ADF test to list of timeseries objects and store the p-value
Hypothesis: Stationary
```{r}
atm.p_value <- c()
for (i in 1:10626) {
  p_value.temp <- adf.test(atm.ts.train[[i]], 'stationary')[[4]]
  atm.p_value[i] <- p_value.temp
}
```

```{r}
mean(atm.p_value, na.rm = TRUE)
median(atm.p_value, na.rm = TRUE)
min(atm.p_value, na.rm = TRUE)
max(atm.p_value, na.rm = TRUE)
```

-> Timeseries data is mostly non-stationary

Remove the non-stationary data and create new list with only stationary data
```{r}
atm.ts.stationary <- list()
k <- 1
for (i in 1:10626) {
  p_value <- atm.p_value[i]
  if(is.na(p_value)) next
  if (TRUE && p_value <= 0.05){
    atm.ts.stationary[[k]] <- atm.ts.train[[i]]
    k <- k+1
  }
}
```


Create a function to fit ARIMA with timeseries
```{r}
runArima <- function(ts){
  model <- auto.arima(ts, seasonal = TRUE)
  return(forecast(model, h=6))
}
```

Fit model and match prediction with existing split data from train dataset
```{r}
atmtstestp <- list()
for (i in 1:10626) {
  days <- length(atm.ts.test[[i]])
  prediction <- c()
  fitted.Vector <- fitted(runArima(atm.ts.train[[i]]))
  if(length(fitted.Vector) < days) next
  for (j in 1:days) {
    prediction[j] <- fitted.Vector[j]
  }
  atmtstestp[[i]] <- data.frame(no=i,pred=prediction,real=atm.ts.test[[i]])
}
```

Calculate MAPE for each ATM
```{r}
for(i in 1:10626){
  atmtstestp[[i]]$mape <- MAPE(atmtstestp[[i]]$pred,atmtstestp[[i]]$real)
}
```


Import test dataset
```{r}
atm.test <- read.table('D:/Sena/Projects/Finhacks/atm_test.csv', sep = ';', header=T)
atm.test.grouped <- split(atm.test, f = atm.test$no..ATM)
```

Fit model and deploy to test dataset
```{r}
for (i in 1:10626) {
  days <- length(atm.test.grouped[[i]]$date)
  prediction <- c()
  fitted.Vector <- fitted(runArima(atm.ts[[i]]))
  if(length(fitted.Vector) < 7) next
  for (j in 1:days) {
    prediction[j] <- fitted.Vector[j]
  }
  atm.test.grouped[[i]]$prediction <- prediction
}
```



